A bad day of studying is better than a good day of sleeping

### 2020-12-25 paper/paper.tex
feat: example for one step revision

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\renewcommand{\thedefinition}{\arabic{definition}}

@@

% TODO write formal background
\section{Formal background}

@@

% TODO write chapter
\subsection{Belief sets and epistemic states}
A belief set is the deductively closed set of propositions an agent accepts as true at any given point in time \cite{Ferme2011}. AGM theory \cite{Alchourron1985} defines postulates for belief sets and their contraction, revision or expansion with new evidence.
% TODO explain contraction, revision, expansion?
%    As our perception of the world described by the knowledge base
%    changes, the knowledge base must be modified. G~irdenfors [9] distinguishes
%    several kinds of modifications. If we simply acquire additional knowledge
%    about the world, and the new knowledge does not conflict with the current
%    beliefs t of the KB, we expand the KB. If, however, the new knowledge is
%    inconsistent with the old beliefs, and we want the KB to be always consistent,
%    we must resolve the conflict somehow; this operation will be called revision. A
%    * Part of this work was performed while this author was visiting the University of Toronto.
%    ** This author is partially supported by the Natural Science and Engineering Research Council
%    of Canada.
%    1 We use the terms belief and knowledge interchangeably in this paper.
%    0004-3702/91/$03.50 © 1991 -- Elsevier Science Publishers B.V. All rights reserved 
%    264 H. Katsuno, A.O. Mendelzon
%    different kind of change occurs when a sentence previously believed becomes
%    questionable and has to be given up; the operation that makes this change is a
%    contraction. Other kinds of operations are discussed in [14].

@@

% do we need to discuss this in ore detail? faithful assignment here:
%Katsuno and Mendelzon [17] propose that an epistemic state Ψ
%should be equipped with an ordering ≤Ψ of the worlds (interpretations), where the compatibility with Bel(Ψ) is ensured by the socalled faithfulness.
%Definition 1 (Faithful Assignment [17]) A function Ψ 
%→≤Ψ that
%maps each epistemic state to a total preorder on interpretations is
%said to be a faithful assignment if and only if:
%(FA1) if ω1 ∈ Ψ and ω2 ∈ Ψ, then ω1 Ψ ω2
%(FA2) if ω1 ∈ Ψ and ω2 ∈  / Ψ, then ω1 <Ψ ω2
%Intuitively, ≤Ψ orders the worlds by plausibility, such that the minimal worlds with respect to ≤Ψ are the most plausible worlds.

@@

% TODO write chapter
\section{Additional metadata for tpo revision}
\subsection{Enriching epistemic states}
Based on DP-AGM and the postulates $(CR1)$-$(CR4)$ Booth and Meyer assume a fixed tpo $\leq$ over a set of worlds $W$ that acts as a plausibility ordering. The goal of the paper is the discussion of functions $\ast$ that return a new ordering $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$. Functions $\ast$ that can be used for iterated revision in that way are refered to as revision operators for $\leq$.

@@

                    5 1 empty $x_{4}^{+}$
                    7 1 empty $x_{4}^{-}$

                    3 2 empty $x_{3}^{+}$
                    5 2 empty $x_{3}^{-}$

                    2 3 empty $x_{2}^{+}$
                    4 3 empty $x_{2}^{-}$

                    1 4 empty $x_{1}^{+}$
                    3 4 empty $x_{1}^{-}$
                    };
            \end{axis}
        \end{tikzpicture}
        \label{fig:example-visualisation-scatterplot}
            \caption{Representation of $\preceq$ over $W^{\pm}$ using sticks}
    \end{figure}

    In this visualisation the worlds on lower ranks (more on the left) are preferred and therefor assumed to be more plausible. Here for example $x_{1}^{+} \prec x_{2}^{+}$ and $x_{3}^{-} \sim x_{4}^{+}$ Note that while all sticks have the same length in this example that is not required.
\end{example}

@@

% visual example with alien -> revise tpo

% show also: new evidence that does not become part of the belief set -> non prio example, explain what it is
\subsection{The problem of just moving things one up}

%\begin{itemize}
%    \item Introduction of $\ast$ as revision operator for $\leq$ and definition of $\ast_{\preceq}$ as example with visualisation.

>>>>

\theoremstyle{definition}
\newtheorem{definition}{Definition}

@@

\section{Formal background}

@@

\subsection{Belief sets and epistemic states}
A belief set is the deductively closed set of propositions an agent accepts as true at any given point in time \cite{Ferme2011}. AGM theory \cite{Alchourron1985} defines postulates for belief sets and their contraction, revision or expansion with new evidence.
% TODO explain contraction, revision, expansion?
%    As our perception of the world described by the knowledge base
%    changes, the knowledge base must be modified. G~irdenfors [9] distinguishes
%    several kinds of modifications. If we simply acquire additional knowledge
%    about the world, and the new knowledge does not conflict with the current
%    beliefs t of the KB, we expand the KB. If, however, the new knowledge is
%    inconsistent with the old beliefs, and we want the KB to be always consistent,
%    we must resolve the conflict somehow; this operation will be called revision. A
%    * Part of this work was performed while this author was visiting the University of Toronto.
%    ** This author is partially supported by the Natural Science and Engineering Research Council
%    of Canada.
%    1 We use the terms belief and knowledge interchangeably in this paper.
%    0004-3702/91/$03.50 © 1991 -- Elsevier Science Publishers B.V. All rights reserved 
%    264 H. Katsuno, A.O. Mendelzon
%    different kind of change occurs when a sentence previously believed becomes
%    questionable and has to be given up; the operation that makes this change is a
%    contraction. Other kinds of operations are discussed in [14].

@@

% TODO: do we need to discuss this in ore detail? faithful assignment here:
%Katsuno and Mendelzon [17] propose that an epistemic state Ψ
%should be equipped with an ordering ≤Ψ of the worlds (interpretations), where the compatibility with Bel(Ψ) is ensured by the socalled faithfulness.
%Definition 1 (Faithful Assignment [17]) A function Ψ 
%→≤Ψ that
%maps each epistemic state to a total preorder on interpretations is
%said to be a faithful assignment if and only if:
%(FA1) if ω1 ∈ Ψ and ω2 ∈ Ψ, then ω1 Ψ ω2
%(FA2) if ω1 ∈ Ψ and ω2 ∈  / Ψ, then ω1 <Ψ ω2
%Intuitively, ≤Ψ orders the worlds by plausibility, such that the minimal worlds with respect to ≤Ψ are the most plausible worlds.

@@

\section{Additional metadata for tpo revision}
\subsection{Enriching epistemic states}
Based on DP-AGM and the postulates $(CR1)$-$(CR4)$ Booth and Meyer assume a fixed tpo $\leq$ over a set of worlds $W$ that acts as a plausibility ordering. The goal of the paper is the discussion of functions $\ast$ that return a new ordering $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$. Functions $\ast$ that can be used for iterated revision in that way are refered to as revision operators for $\leq$.

@@

                    3 1 empty $x_{4}^{+}$
                    6 1 empty $x_{4}^{-}$

                    2 2 empty $x_{3}^{+}$
                    5 2 empty $x_{3}^{-}$

                    1 3 empty $x_{2}^{+}$
                    3 3 empty $x_{2}^{-}$

                    1 4 empty $x_{1}^{+}$
                    3 4 empty $x_{1}^{-}$
                    };
            \end{axis}
        \end{tikzpicture}
        \caption{Representation of $\preceq$ over $W^{\pm}$ using sticks}
        \label{fig:example-visualisation-scatterplot}
    \end{figure}

    In this visualisation the worlds on lower ranks (more on the left) are preferred and therefor assumed to be more plausible. Here for example $x_{1}^{+} \prec x_{3}^{+}$ and $x_{1}^{-} \sim x_{4}^{+}$ Note that while all sticks have the same length in this example that is not required.
\end{example}

@@

\begin{example}
    \label{example:example-updated-tpo}
    Reconsidering the tpo $\preceq$ from example \ref{example:example-stick} (page \pageref{example:example-stick}). When a new piece of evidence $\alpha$ has to be considered each world gets mapped to one end of the interval assigned to it depending on if it is an $\alpha$-world or not. In figure \ref{fig:example-updated-tpo} that mapping is indicated by the filled out dot. For this example $x_{1}, x_{2}$ and $x_{3}$ are $[\neg\alpha]$-worlds while $x_{4}$ is an $[\alpha]$-world.

    \begin{figure}[h]
        \centering
        \begin{tikzpicture}[scale=1.2]
            \begin{axis}[
                  yticklabels={,,$x_{4}$,$x_{3}$,$x_{2}$,$x_{1}$},
                  xticklabels={,,},
                  ytick style={draw=none},
                  xtick style={draw=none},
                  axis line style={draw=none}
            ]
            \addplot[
                scatter,
                scatter src=explicit symbolic,
                mark size=3,
                scatter/classes={
                    empty={mark=o, draw=black}
                },
                nodes near coords*={\Label},
                visualization depends on={value \thisrow{label} \as \Label}
            ]
            table [meta=class] {
                    x y class label

                    3 1 filled $x_{4}^{+}$
                    6 1 empty $x_{4}^{-}$

                    2 2 empty $x_{3}^{+}$
                    5 2 filled $x_{3}^{-}$

                    1 3 empty $x_{2}^{+}$
                    3 3 filled $x_{2}^{-}$

                    1 4 empty $x_{1}^{+}$
                    3 4 filled $x_{1}^{-}$
                    };
            \end{axis}
        \end{tikzpicture}
        \caption{Associating worlds with their positive/negative representations}
        \label{fig:example-updated-tpo}
    \end{figure}

    The updated tpo $\leq_{\alpha}^{\ast}$ can now be inferred from the figure as the ordering of the filled dots representing the new assignment for the respective world: $x_{1} \sim x_{2} \sim x_{4} < x_{3}$.
\end{example}

\subsection{Non priotised revision}
% show also: new evidence that does not become part of the belief set -> non prio example, explain what it is
\subsection{The problem of just moving things one up}
